---
title: "10.5 Exercises"
output:
  html_document:
    df_print: paged
---
10.5 Exercises

1. How can you tell if an object is a tibble? (Hint: try printing mtcars, which is a regular data frame).

data frame will try to print all rows while tibble just first 10 by default

```{r}
mtcars
```

```{r}
tb_mtcars <- as_tibble(mtcars)
tb_mtcars
```


2. Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviours cause you frustration?

```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```

```{r}
tb <- data.frame(abc = 1, xyz = "a")
tb$x
tb[, "xyz"]
tb[, c("abc", "xyz")]
```

If you have the name of a variable stored in an object, e.g. var <- "mpg", how can you extract the reference variable from a tibble?

Practice referring to non-syntactic names in the following data frame by:

    Extracting the variable called 1.

    Plotting a scatterplot of 1 vs 2.

    Creating a new column called 3 which is 2 divided by 1.

    Renaming the columns to one, two and three.

annoying <- tibble(
  `1` = 1:10,
  `2` = `1` * 2 + rnorm(length(`1`))
)

What does tibble::enframe() do? When might you use it?

What option controls how many additional column names are printed at the footer of a tibble?

```{r}
plot(cars)
```

